---
title: "p8105_hw2_cx2227"
author: "Chuyue Xiang"
date: "10/1/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

## Problem 1

### Part 1: Read and clean the Mr. Trash Wheel sheet
```{r}
trashwheel = read_excel("Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "Mr. Trash Wheel",
                        range = "A2:N406", na = "") %>%
  janitor::clean_names() %>%
  na.omit() %>% 
  mutate(sports_balls = as.integer(round(sports_balls, 0)))
```

### Part 2: Read and clean precipitation data for 2017 and 2018

#### Read and clean 2017 precipitation data
```{r}
precip_2017 = read_excel("Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2017 Precipitation", 
                         range = "A2:B14", na = "" ) %>%
  mutate(year = 2017)
```


#### Read and clean 2018 precipitation data
```{r}
precip_2018 = read_excel("Trash-Wheel-Collection-Totals-8-6-19.xlsx", sheet = "2018 Precipitation", 
                         range = "A2:B14", na = "" ) %>%
  mutate (year = 2018)
```

#### Combine 2017 and 2018 data
```{r}
combine_precip = left_join(precip_2017, precip_2018, by = "Month") %>%
  mutate(Month = month.name)
```

### Part 3: Paragraph

- The trashwheel dataset has `r nrow(trashwheel)` observations and the combined precipitation table has `r nrow(combine_precip)` obeservations.
- The key variable of the trashwheel dataset is variable "sports_balls", and the key variable fo the combined precipitation table is variable total precipitation amount.
- The total precipitation in 2018 is `r sum(pull(precip_2018, Total))` (in).
- The median number of sports balls in a dumpster in 2017 is `r median(pull(filter(trashwheel, year == 2017), sports_balls))`


## Problem 2

### Part 1: Clean the data in pols-month.csv.

```{r, message = FALSE, warning=FALSE}
plos_month = read_csv("./fivethirtyeight_datasets/pols-month.csv") %>%
  separate(col = mon, into = c("year","month","day")) %>%
  mutate(month = recode(month, "01" = "January", "02" = "February", "03" = "March", "04" = "April",
                        "05" = "May", "06" = "June", "07" = "July", "08" = "August", "09" = "September",
                        "10" = "October", "11" = "November", "12" = "December")) %>% 
  select(prez_gop, prez_dem, everything()) %>%
  pivot_longer(prez_gop:prez_dem, names_to = "president", names_prefix = "prez_") %>% 
  filter(value != 0) %>% 
  select(-day) %>%
  select(-value)
```

### Part 2: Clean the data in snp.csv.

```{r, message = FALSE, warning=FALSE}
snp = read_csv("./fivethirtyeight_datasets/snp.csv") %>% 
  separate(col = date, into = c("month","day","year")) %>% 
  arrange(as.integer(year), as.integer(month)) %>% 
  select(year, month, close) %>% 
  mutate(month = recode(month, "1" = "January", "2" = "February", "3" = "March", "4" = "April",
                        "5" = "May", "6" = "June", "7" = "July", "8" = "August", "9" = "September",
                        "10" = "October", "11" = "November", "12" = "December"))
```

### Part 3: Tidy the unemployment data.

```{r, message = FALSE, warning=FALSE}
unemployment = read_csv("./fivethirtyeight_datasets/unemployment.csv") %>% 
  pivot_longer(Jan:Dec, names_to = "month", values_to = "value") %>% 
  mutate(month = recode(month, "Jan" = "January", "Feb" = "February", "Mar" = "March", "Apr" = "April",
                        "May" = "May", "Jun" = "June", "Jul" = "July", "Aug" = "August", "Sep" = "September","Oct" = "October", "Nov" = "November", "Dec" = "December")) %>%
  mutate(Year = as.character(Year)) %>% 
  select(year = Year, everything())
```

